Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-25 paper/paper.tex
What we need to write for the algorithm

\Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.
As well as the modifications to solve $k$-less and induced problems, we have made two
simplifications: we do not use conflict-directed backjumping, and we do not use iterated label
filtering to recalculate neighbourhood degree sequences if vertices are not present in any target
domain after construction---in preliminary experiments, these techniques were not beneficial for $k
> 0$. We also do not strip isolated vertices, as this is not a valid simplification in the induced
case.

To handle wildcards, we include $k$ additional $\bot$ values in domains, rather than a single value
which may be used $k$ times. These are treated as having degree zero, in an attempt to maximising
the expected number of solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This
technique allows us to retain the bit-parallel all different propagator used in the original
algorithm. However, we must be careful to treat domains containing multiple wildcard values (which
we call ``effectively unit'') specially during unit propagation (line~\ref{line:effect}), and we
introduce a symmetry break (line~\ref{line:sym}) to try only a single wildcard value for each
variable.

To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
using path reasoning on complement graphs, but this is expensive to calculate and provides little
benefit in practice on the instances we considered.

>>>>

\Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.

The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
the pattern graph, each of which has a domain containing one value for every vertex in the target
graph.

In lines ?? we use the reasoning from section ?? to eliminate infeasible initial values from the
domains. We do not use iterated label filtering ?? cite to recalculate neighbourhood degree
sequences if any vertices are not present in any target domain after construction: preliminary
experiments indicated that this happened very rarely.

To handle unmapped vertices, on line ?? we include $k$ additional wildcard $\bot$ values in each
domain (rather than a single value which may be used $k$ times).

?? Constraints and unit propagation

?? Supplemental graphs. These are also used for eliminating infeasible values.

?? All different

We must be careful to treat domains containing multiple wildcard values (which we call ``effectively
unit'') specially during unit propagation (line~\ref{line:effect}), and we introduce a symmetry
break (line~\ref{line:sym}) to try only a single wildcard value for each variable.

?? Search. No backjumping.

?? Heuristics

Wildcards are treated as having degree zero, in an attempt to maximising the expected number of
solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This technique allows us to
retain the bit-parallel all different propagator used in the original algorithm.

?? As well as the modifications to solve $k$-less and induced problems, we have made two
simplifications: we do not use conflict-directed backjumping, and in preliminary experiments, these
techniques were not beneficial for $k > 0$.

To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
using path reasoning on complement graphs, but this is expensive to calculate and provides little
benefit in practice on the instances we considered.  We also do not strip isolated vertices as
cite?? did, as this is not a valid simplification in the induced case.
